Supplemental Material for submission ``Do Objects in Real-World Images Have a Canonical Name?''

### 2019-05-17 papers/EMNLP2019/analysis.tex
updated analysis table

\subsection{Measures}

@@

\begin{itemize}
\item \textbf{\% top}: the average relative frequency of the most frequent response (shown in percent)
\item \textbf{$H$}: the $H$ agreement measure used previously in the psycholinguistic literature
\cs{How is this defined?}
%\item \textbf{N}: the average number of types in the response set of ManyNames
%\item \textbf{N$_{>1}$}: the average number of types, excluding types that have been annotated only once
\cs{alternatively we could show a plot going from 1 to, let's say, $>10$}
\item \textbf{top=VG}: the proportion of items where the top response in ManyNames corresponds to the VisualGenome name
\item \textbf{\% VG}: the average relative frequency of the VisualGenome name in the response set

@@

\subsection{Results}

@@

\gbt{Super-interesting results.}
Finally, the category-level agreement figures tell yet another story: when aggregating the responses for all objects with the same VisualGenome synset, we obtain on average 30 types (with $N_{>1})$, i.e. variants of the original VG class. 
Surprisingly, here, only 32.7\% of the aggregated response sets still have the VG name as the most frequent response, which means that for 70\% of the VG names, annotators in ManyNames, on average, prefer a different name.  
Likewise, the relative frequency of the top response drops considerably and $H$ increases from 1.3 for instance-level agreement to 2.4 on object-level agreement.  
\cs{Can we say more about what's going on in the people and vehicles domain, category-level, top=VG? E.g., put corresponding examples in Tab.\ref{tab:qual}}
%
\subsection{Discussion (for now)}
What does this discrepancy between the instance-level and category-level agreement in VisualGenome and ManyNames naming choices mean? 
First of all, it suggests that the same original VisualGenome name can trigger very different variants depending on the visual instance, leading to a drastic increase of variants elicited for categories as compared to instances.
Second, this clearly shows that annotators in VG do not generally annotate the most canonical name \cs{but they don't annotate the name, but the description} and that many names annotated for objects in VG do not correspond to the overall most preferred variant. \sz{think more ...}
\gbt{I don't think we can conclude this second part -- we do have the 70\% top=VG figure that says that VG annotators annotate the most canonical name. What this suggests to me is that instance-level properties are more important than category-level properties, somehow.
  That is, there are systematic properties of instances that make them have a single most salient name.
  However, I expect that this result will be very influenced by referential uncertainty (in single images, it will mostly be clear that it's a man, but in some it may be unclear \ra high instance agreement, low category agrement.}
\cs{I don't think that 70\% is high. E.g., the ResNet has a top-1 error rate of 25\% on ILSVRC 2015.}

\begin{tabular}{lcccc|cccc}
\toprule
 & \multicolumn{4}{c|}{Instance-level agreement} & \multicolumn{4}{c}{Class-level agreement}\\ 
         domain &         \%top &    H &       top=VG &          \%VG &         \%top &    H &       top=VG &          \%VG \\
\midrule
            all &  78.5 (21.5) &  0.7 &  72.8 (44.5) &  65.1 (36.1) &  58.9 (21.9) &  1.8 &  32.7 (46.9) &  23.2 (27.1) \\
 animals\_plants &  95.8 (11.4) &  0.1 &         93.8 &         92.1 &  74.3 (22.5) &  1.0 &         29.5 &         25.8 \\
      buildings &  79.0 (21.1) &  0.7 &         72.6 &         64.8 &  53.5 (19.4) &  2.2 &         32.3 &         22.1 \\
           home &  76.3 (20.6) &  0.8 &         78.5 &         67.0 &  56.4 (20.3) &  2.1 &         45.9 &         29.9 \\
           food &  79.8 (20.5) &  0.7 &         62.9 &         57.0 &  52.7 (21.1) &  1.9 &         31.1 &         20.8 \\
       vehicles &  79.0 (19.9) &  0.6 &         71.1 &         65.6 &  58.6 (17.0) &  1.7 &         21.4 &         21.1 \\
         people &  64.4 (21.8) &  1.2 &         49.8 &         39.3 &  51.1 (19.6) &  2.2 &         24.4 &         12.9 \\
       clothing &  73.9 (18.5) &  0.9 &         70.2 &         60.2 &  56.2 (17.2) &  1.9 &         40.5 &         26.0 \\
\bottomrule
\end{tabular}

\caption{Agreement in naming measured on the level of instances and on the level of VG classes (i.e.\ after grouping objects by their VG synset), for filtered response sets (frequency threshold of 3)}
\label{tab:agree}
\end{table*}

\subsection{Qualitative Analysis}

@@

>>>>

\subsection{Agreement}

@@

\begin{itemize}
\item \textbf{\% top}: the average relative frequency of the most frequent response (shown in percent)
\item \textbf{$H$}: the $H$ agreement measure used previously in the psycholinguistic literature
\cs{How is this defined?}
\begin{equation}
H = \sum_{i=1}^k p_i\ log_2(1/p_i)
\end{equation}

\item \textbf{N}: the average number of types in the response set of ManyNames
%\item \textbf{N$_{>1}$}: the average number of types, excluding types that have been annotated only once
\cs{alternatively we could show a plot going from 1 to, let's say, $>10$}
\item \textbf{top=VG}: the proportion of items where the top response in ManyNames corresponds to the VisualGenome name
\item \textbf{\% VG}: the average relative frequency of the VisualGenome name in the response set

@@

@@

\gbt{Super-interesting results.}
Finally, the category-level agreement figures tell yet another story: when aggregating the responses for all objects with the same VisualGenome synset, we obtain on average 30 types (with $N_{>1})$, i.e. variants of the original VG class. 
Surprisingly, here, only 32.7\% of the aggregated response sets still have the VG name as the most frequent response, which means that for 70\% of the VG names, annotators in ManyNames, on average, prefer a different name.  
Likewise, the relative frequency of the top response drops considerably and $H$ increases from 1.3 for instance-level agreement to 2.4 on object-level agreement.  
\cs{Can we say more about what's going on in the people and vehicles domain, category-level, top=VG? E.g., put corresponding examples in Tab.\ref{tab:qual}}
%

\paragraph{Qualitative Analysis}

@@

\subsection{Discussion (for now)}
What does this discrepancy between the instance-level and category-level agreement in VisualGenome and ManyNames naming choices mean? 
First of all, it suggests that the same original VisualGenome name can trigger very different variants depending on the visual instance, leading to a drastic increase of variants elicited for categories as compared to instances.
Second, this clearly shows that annotators in VG do not generally annotate the most canonical name \cs{but they don't annotate the name, but the description} and that many names annotated for objects in VG do not correspond to the overall most preferred variant. \sz{think more ...}
\gbt{I don't think we can conclude this second part -- we do have the 70\% top=VG figure that says that VG annotators annotate the most canonical name. What this suggests to me is that instance-level properties are more important than category-level properties, somehow.
  That is, there are systematic properties of instances that make them have a single most salient name.
  However, I expect that this result will be very influenced by referential uncertainty (in single images, it will mostly be clear that it's a man, but in some it may be unclear \ra high instance agreement, low category agrement.}
\cs{I don't think that 70\% is high. E.g., the ResNet has a top-1 error rate of 25\% on ILSVRC 2015.}

\begin{tabular}{lccccc|ccccc}
\toprule
 & \multicolumn{5}{c|}{Instance-level agreement} & \multicolumn{5}{c}{Class-level agreement}\\ 
          domain &    N &         \%top (std) &          H (std) & top=VG &   \%VG &     N &         \%top (std) &          H (std) & top=VG &   \%VG \\
\midrule
            all &  2.9 &  75.2 (21.9) &  0.9 (0.7) &   72.8 &  62.8 &  29.7 &  56.4 (21.5) &  2.0 (1.0) &   32.7 &  23.4 \\
       vehicles &  2.4 &  76.6 (19.8) &  0.8 (0.6) &   71.1 &  63.9 &  33.2 &  57.4 (17.3) &  1.8 (0.6) &   21.4 &  21.2 \\
      buildings &  3.0 &  74.7 (20.7) &  1.0 (0.7) &   72.6 &  61.6 &  31.3 &  51.0 (18.8) &  2.4 (0.9) &   32.3 &  22.2 \\
       clothing &  3.2 &  70.1 (18.5) &  1.1 (0.6) &   70.2 &  57.4 &  34.1 &  53.4 (16.6) &  2.1 (0.8) &   40.5 &  26.1 \\
           home &  3.1 &  72.6 (20.7) &  1.0 (0.7) &   78.5 &  64.1 &  48.8 &  54.0 (19.4) &  2.3 (1.0) &   45.9 &  29.9 \\
         people &  4.3 &  59.0 (20.4) &  1.5 (0.7) &   49.8 &  36.3 &  53.4 &  47.5 (17.2) &  2.5 (0.9) &   24.4 &  13.0 \\
           food &  2.9 &  76.4 (20.7) &  0.9 (0.7) &   62.9 &  55.2 &  15.2 &  50.8 (20.3) &  2.0 (0.8) &   31.1 &  20.8 \\
 animals\_plants &  1.5 &  94.5 (12.1) &  0.2 (0.4) &   93.8 &  91.0 &  12.4 &  71.3 (23.3) &  1.2 (0.9) &   29.5 &  26.1 \\
\bottomrule
\end{tabular}

\caption{Agreement in naming measured on the level of instances and on the level of VG classes (i.e.\ after grouping objects by their VG synset), for filtered response sets (frequency threshold of 2)}
\label{tab:agree}
\end{table*}
